The Problem of Heads of a Fighting Force from Long Ago

### 2013-02-10 byzantine/byzantine.tex
byzantine: rewrite abstract

\begin{abstract}
Groups of computers that you can trust must handle broken parts that give facts
that don't agree to different parts of the group. This situation can be talked
about by pretending about the heads of a fighting force from long ago, who are
waiting with their people around a bad guy city. Talking to each other
only by a person who carries a letter, the people must agree upon a shared
fighting plan. However, one or more of them may be bad guys who will try to
confuse the others.
The problem is to find a plan to make sure that the good guys will agree on
something.  It is shown that, using only spoken letters, this problem is
possible if and only if more than two thirds of the heads are good guys; so a
single bad guy can confuse two good guys.  With written letters which can't be
pretended, the problem is possible for any number of heads and possible bad
guys. Ways to use the plans that are answers are then talked about.
\end{abstract}

>>>>

\begin{abstract}
Sometimes, in a group of computers, there will be a broken part that will tell
confusing facts to the rest of the computers in the group. If we want to be
able to trust the entire group, it must be able to ignore these confusing facts
when deciding what to do. We can talk about this situation by playing
make-believe about the heads of a fighting force from long ago, who are waiting
with their people around a bad guy city. The people must agree upon a shared
fighting plan, but can only talk to each other by sending a person who carries
a letter. However, one or more of the heads may be bad guys who will try to
confuse the others. The problem is to find a way for the good guys to talk to
each other, without knowing who the bad guys are, to make sure they can agree
on what to do anyway. We will show that, if the good guys use only
word-of-mouth, this problem is possible if and only if more than two-thirds of
the heads are good guys. This means that a single bad guy could confuse two
good guys. If the good guys use signed written letters, which means a bad guy
couldn't pretend their letter came from someone else, the problem is possible
for any number of heads and possible bad guys.
Finally we will talk about ways to use the plans that are answers to this
problem in different situations in the real world.
\end{abstract}
